\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-12-06 RA-L/theoryCorrelation.tex
slight updates to plot

\subsection{Efficient Control of Correlation}
%A set of simulations were conducted to demonstrate the importance of boundary friction.  
This section examines maximum correlation values as a function of  $w,L$ using \eqref{eq:correlationFriction}
from Section  \ref{subsec:ClosedLoopCovarianceControl}. 
The maximum correlation using boundary layer friction $\displaystyle  \max_{w,L} \left( \rho(A,h,w,L) \right)$ can be found by gradient descent, as shown in Fig.~\ref{fig:ControlledCorrelation}. 
For swarms with small area, this method enables generating the full range of correlations $\pm 1$, while the stable configuration method from Section \ref{sec:theory} could only generate correlations $\pm 1/2$.  As  the swarm area $A$ increases above $\approx 0.43$, the stable configuration method is more effective.
Larger boundary layers $h$ enable more control of correlation.

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation under the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}
\end{figure}

>>>>

\subsection{Efficient Control of Correlation}
%A set of simulations were conducted to demonstrate the importance of boundary friction.  
This section examines maximum correlation values as a function of  $w,L$ using \eqref{eq:correlationFriction}
from Section  \ref{subsec:ClosedLoopCovarianceControl}. 
The maximum correlation using boundary layer friction $\displaystyle  \max_{w,L} \left( \rho(A,h,w,L) \right)$ can be found by gradient descent, as shown in Fig.~\ref{fig:ControlledCorrelation}. 
For swarms with small area, this method enables generating the full range of correlations $\pm 1$, while the stable configuration method from Section \ref{sec:theory} could only generate correlations $\pm 1/2$.  As  the swarm area $A$ increases above $\approx 0.43$, the stable configuration method is more effective.
Larger boundary layers $h$ enable more control of correlation.
The multimedia attachment shows efficient control of correlation with simulations using the 2D physics engine Box2D~\citep{catto2010box2d} and 144 disc-shaped robots with boundary layer model \eqref{eq:boundarylayerflow}.

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation $\rho_{xy}$ under the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}
\end{figure}
